### 2016-09-16 doc/manuscript.Rmd
Rearranged tabs and figs, put placeholoder captions in

```{r caption_setup}
## Include captions below using `captioner` package
fig <- captioner::captioner(prefix = 'Figure')
cite_f <- pryr::partial(fig, display = 'cite')
sfig <- captioner::captioner(prefix = 'Supplemental Figure')
cite_sf <- pryr::partial(sfig, display = 'cite')
tab <- captioner::captioner(prefix = 'Table')
cite_t <- pryr::partial(tab, display = 'cite')
stab <- captioner::captioner(prefix = 'Supplemental Table')
cite_st <- pryr::partial(stab, display = 'cite')
# usage: cite_st('basicChar')

fig_gee <- fig('gee', 'caption here')
fig_consort <- fig('consort', 'caption here')
```

```{r analyze_gee, cache=TRUE}
gee_adj_df <- analyze_gee()
gee_unadj_df <- analyze_gee(covars = "VN")
```

@@

# Tables and figures

@@

```{r fig_dist}
plot_tagfa()
```

```{r table_dist}
table_tagfa()
```

@@

```{r table_corr}
#table_corr(cor_results)
```

```{r fig_gee}
plot_gee_main(gee_unadj_df)
plot_gee_main(gee_adj_df)
```

```{r table_gee_main}
table_gee_main(gee_unadj_df)
table_gee_main(gee_adj_df)
```

>>>>

```{r caption_setup}
## Include captions below using `captioner` package
fig <- captioner::captioner(prefix = 'Figure')
cite_f <- pryr::partial(fig, display = 'cite')
sfig <- captioner::captioner(prefix = 'Supplemental Figure')
cite_sf <- pryr::partial(sfig, display = 'cite')

tab <- captioner::captioner(prefix = 'Table')
cite_t <- pryr::partial(tab, display = 'cite')
stab <- captioner::captioner(prefix = 'Supplemental Table')
cite_st <- pryr::partial(stab, display = 'cite')
# usage: cite_st('basicChar')

tab_qic <- tab('qic', 'caption here')
tab_basic <- tab('basic', 'caption here')
tab_tagfa <- tab('tagfa', 'caption here')
tab_gee <- tab('gee', 'caption here')

fig_consort <- fig('consort', 'caption here')
fig_tagfa <- fig('tagfa', 'caption here')
fig_heatmap <- fig('heatmap', 'caption here')
fig_gee_unadj <- fig('gee_unadj', 'caption here')
fig_gee_adj <- fig('gee_adj', 'caption here')
fig_pls <- fig('pls', 'caption here')
```

```{r analyze_gee, cache=TRUE}
gee_unadj_df <- analyze_gee(covars = "VN")
gee_adj_df <- analyze_gee()
```

@@

# Tables

```{r table_tagfa}
table_tagfa()
```

```{r table_gee}
table_gee_main(gee_unadj_df)
table_gee_main(gee_adj_df)
```

# Figures

@@

```{r fig_tagfa}
plot_tagfa()
```

@@

```{r fig_gee_unadj}
plot_gee_main(gee_unadj_df)
```

```{r fig_gee_adj}
plot_gee_main(gee_adj_df)
```
